\documentstyle[11pt]{article}
\renewcommand{\oddsidemargin}{0pt}
\renewcommand{\evensidemargin}{0pt}
\renewcommand{\topmargin}{0pt}
\renewcommand{\headheight}{0pt}
\renewcommand{\headsep}{0pt}
\renewcommand{\textwidth}{468pt}
\renewcommand{\textheight}{260mm}
\hoffset=-60pt
\voffset=-36pt
%
\settowidth{\parindent}{}
\setlength{\parskip}{2mm}
%
\newcommand{\dvd}{\rule{30mm}{0.2mm}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\beqn}{\begin{eqnarray}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\eeqn}{\end{eqnarray}}
\newcommand{\lsf}{\large \sf}
%
\newcommand{\qbar}{\mbox{$\overline{q}$}}
% \pagestyle{empty}
\pagenumbering{arabic}
%
\begin{document}
%
%\twocolumn
%____________________________________________________________________________
\vspace*{0.25in}
\begin{center}
\LARGE \bf Daryl E. Herzmann\\
\Large \bf Biosketch\\
\end{center}
\begin{tabbing}
\= \Large \bf Contact Information \hspace*{2.5in} \= \\
\> \> \\
\> \lsf Department of Agronomy \> \lsf Phone : (515)294-5978\\
\> \lsf Iowa State University \> \lsf Fax: (515)294-3163\\
\> \lsf Ames, IA 50011 \> \lsf Email: akrherz@iastate.edu \\
\end{tabbing}
\Large \bf Professional Preparation
\normalsize \sf
\begin{itemize}
\item B.A., 2001, Iowa State University.  Meteorology Major.
\end{itemize}
%\vspace*{0.25in}
\Large \bf Appointments\\ \\
\normalsize \bf Iowa State University, October 1997 - present
\normalsize \sf
\begin{itemize}
\item August 2001 - present: Systems Analyst III, Iowa State University.\\
 \textbf{Supervisors}: Dr Dennis Todey (2001-2004), Dr Raymond Arritt (2004-2018) and Dr Rick Cruse (2018-).  \\
\textbf{Iowa Environmental Mesonet}: Develop an environmental data collection
platform to support the research and outreach activities of the University.
Determine and execute new approaches to data collection and dissemination 
through a feature rich website.  Manage the day to day support demands 
created by the large number of core partners and general public. \\
\textbf{Department of Agronomy}: Collaborate on multi-disciplinary research
times providing computational and meteorological expertise to the groups. \\
\textbf{Grant-Supported Research} Manage High Performance Computing platforms
to support the research activities of Ag-Meteorology group.  Design, 
implement, and administer computing and storage platforms.
\end{itemize}
%end employment
%

\Large \bf Products\\ \\
\normalsize \bf Papers
\normalsize \sf
\begin{itemize}
\item Wang, E., R. Cruse, B. Sharma-Acharya, \textbf{D. Herzmann}, B. Gelder, D. James, D. Flanagan, H. Blanco-Canqui, R. Mitchell, D. Laird. Strategic switchgrass (Panicum virgatum) production within row cropping systems: Regional‐scale assessment of soil erosion loss and water runoff impacts. GCB Bioenergy, 2020; 955-967. https://doi.org/10.1111/gcbb.12749 
\item Archontoulis, S. et al. Predicting crop yields and soil‐plant nitrogen dynamics in the US Corn Belt. Crop Science, 2020; 721-738. https://doi.org/10.1002/csc2.20039
\item Cruse, R., \textbf{D. Herzmann}, B. Sharma-Acharya, H. Blanco-Canqui, and B. Gelder. The Daily Erosion Project: Soil erosion impacts of strategic switchgrass (Panicum virgatum) placement in row cropped watersheds. Geophysical Research Abstracts, 2019; 21. 2019EGUGA..2118868C
\item Gelder, B., T. Sklenar, D. James, \textbf{D. Herzmann}, R. Cruse, K. Gesch, and J. Laflen. The Daily Erosion Project–daily estimates of water runoff, soil detachment, and erosion. Earth Surface Processes and Landforms, 2018; 1105-1117. https://doi.org/10.1002/esp.4286
\item Iqbal, Javed, M. Necpalova, S. Archontoulis, R. Anex, M. Bourguignon, \textbf{D. Herzmann}, D. Mitchell, J. Sawyer, Q. Zhu, and M. Castellano. Extreme weather-year sequences have nonadditive effects on environmental nitrogen losses. Global Change Biology, 2017; 24 e303-e317. http://dx.doi.org/10.1111/gcb.13866
\end{itemize}

\normalsize \sf
\normalsize \bf Presentations (Conference/Outreach)
\normalsize \sf
\begin{itemize}
    \item Herzmann, D., 2020. IEM Dog and Pony Show. San Antonio NWS, Ames, IA. Sep. 29, 2020.
    \item Herzmann, D., 2020. IEM and other things. Central Region NWS, Ames, IA. Sep. 22, 2020.
    \item Herzmann, D., 2020. The Weather Bureau and the IEM. Des Moines NWS, Johnston, IA. Feb. 20, 2020.
    \item Herzmann, D., 2020. Providing the E in G x E x M. ISU Agronomy 600B, Ames, IA. Feb. 5, 2020.
\end{itemize}

\vspace*{0.25in}
\Large \bf Synergistic Activities (PIs, Team Size)
\normalsize \sf
\begin{itemize}
\item Iowa Environmental Mesonet (2, 2)\\
2001-2020. Integrating diverse datasets from eight
different observing networks in the state of Iowa.  Program and maintain data
ingestion / manipulation systems to process the data. Exploring and implementing 
new techniques for data visualization and dissemination.  Coordinate with local
agencies with oversight of their observing networks.  Data focalpoint for 
observations in the state of Iowa. Project website generates billions of hits 
from millions of unique internet addresses (users) per month.  Email and 
phone support is given for hundreds of agencies that contact the project each
year.
\item Daily Erosion Project (2, 8)\\
2003-2020. Developing a model system to analyze real-time soil erosion loss over the 
midwestern US.  Responsibilities include the development of the model execution
environment, generation of analysis products, and dissemination of products 
via website.
\end{itemize}
\vspace*{0.25in}
%

% see cv_extension.tex
%

\pagebreak
%____________________________________________________________________________
\end{document}
